Speakers of diverse languages structure their utterances for efficient communication

### 2019-09-06 Paper/paper.Rmd
added prov plots to paper

$$surprisal(w_i|w_{i-1}w_{i-2}...) = -log P(w_i|w_{i-1}w_{i-2}...) = -log P(w_i,w_{i-1}w_{i-2},...)P(w_{i-1}w_{i-2}...)$$

@@

Plot of Providence unigram curves

@@

Plot of Providence bigram and trigram curves

>>>>

$$surprisal(w_i|w_{i-1}w_{i-2}...) = -log P(w_i|w_{i-1}w_{i-2}...)$$
$$= -log \frac{P(w_i,w_{i-1}w_{i-2},...)}{P(w_{i-1}w_{i-2}...)}$$

@@

```{r, echo=F, fig.height =2, fig.cap="Providence frequency-based information curves"}
childes_results %>% 
  filter(Language == "English", context == 0, length %in% c(5, 7, 9)) %>%
  ggplot(aes(x = word_order, y = s, color = speaker_role)) + 
    geom_point() + 
    facet_wrap(~length) + 
    scale_x_continuous(breaks = 1:9) + 
    geom_line() + 
    xlab("Word position") + 
    ylab("Mean information")
```

@@

```{r, echo=F, fig.height =2, fig.cap="Providence context-based information curves"}
childes_results %>% 
  filter(Language == "English", context %in% c(1, 2), length %in% c(5, 7, 9)) %>%
  ggplot(aes(x = word_order, y = s, color = speaker_role)) + 
    geom_point() + 
    facet_wrap(context~length) + 
    scale_x_continuous(breaks = 1:9) + 
    geom_line() + 
    xlab("Word position") + 
    ylab("Mean information")
```

### 2019-09-06 Paper/paper.tex
added prov plots to paper

\[surprisal(w_i|w_{i-1}w_{i-2}...) = -log P(w_i|w_{i-1}w_{i-2}...) = -log P(w_i,w_{i-1}w_{i-2},...)P(w_{i-1}w_{i-2}...)\]

@@

Plot of Providence unigram curves

@@

Plot of Providence bigram and trigram curves

>>>>

\[surprisal(w_i|w_{i-1}w_{i-2}...) = -log P(w_i|w_{i-1}w_{i-2}...)\]
\[= -log \frac{P(w_i,w_{i-1}w_{i-2},...)}{P(w_{i-1}w_{i-2}...)}\]

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{\label{fig:unnamed-chunk-1}Providence frequency-based information curves}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{\label{fig:unnamed-chunk-2}Providence context-based information curves}
\end{figure}
